Summary of the Iberian Bees Database

### 2022-02-28 Manuscript/Summary/Summary.Rmd
Some small edits

```{r eval=FALSE, message=FALSE, warning=FALSE}
#table of
#Name	
#Contact	
#Number of records as main dataholder	
#Number of records as co-dataholder
#email?? Maually :(
#default <- par()$mar
#par(mar = c(13.1, 4.1, 4.1, 2.1))
#barplot(head(sort(table(data2$Authors.to.give.credit), decreasing = TRUE),20), las = 2, cex.names = 0.7)
#par(mar = default)
#Can be done prettier.
#Ideally, we can merge all authors, split and count individually.
library(stringi)
authors <- data$Authors.to.give.credit[which(!is.na(data$Authors.to.give.credit))]
authors[which(authors == "Ornosa, C., Martínez, M. D.")] <- "C. Ornosa, M.D. Martínez"
authors[which(authors == "C. Ornosa & F. J. Ortiz-Sánchez")] <- "C. Ornosa, F. J. Ortiz-Sánchez"
authors[which(authors == "C. Ornosa & M.D. Martínez")] <- "C. Ornosa, M.D. Martínez"
authors[which(authors == "Ortiz-Sanchez, F.J.")] <- "F.J. Ortiz-Sanchez"
authors[which(authors == "Heras, C., Gayubo, S. F.")] <- "C. Heras, S.F. Gayubo"
authors[which(authors == "Ornosa, C.")] <- "C. Ornosa"
authors[which(authors == "Herrera, J.")] <- "Javier Herrera"
authors[which(authors == "Francisco Javier Ortiz-Sánchez, Pedro Coello & Manuel Baena")] <- "Francisco Javier Ortiz-Sánchez, Pedro Coello, Manuel Baena"
authors[which(authors == "González, J. A., Torres, F., Gayubo, S. F.")] <- "J.A. González, , F. Torres, S.F. Gayubo"
authors[which(authors == "Dardón, M. J., Torres, F., Asís, J. D.")] <- "M.J. Dardón, F. Torres, J.D. Asís"
authors[which(authors == "Pérez-Iñigo Mora, C.")] <- "C. Pérez-Iñigo Mora"
authors[which(authors == "Pablo Vargas, Concepción Ornosa, Francisco Javier Ortiz-Sánchez & Juan Arroyo")] <- "Pablo Vargas, Concepción Ornosa, Francisco Javier Ortiz-Sánchez, Juan Arroyo"
authors[which(authors == "C. Heras y S.F. Gayubo")] <- "C. Heras, S.F. Gayubo"
authors[which(authors == "J. L. BLANCO-PASTOR, C. ORNOSA, D. ROMERO, I. M. LIBERAL, J. M. GÓMEZ & P. VARGAS")] <- "J. L. Blanco-Pastor, C. Ornosa, D. Romero, I.M. Liberal, J.M. Gómez, P. Vargas"
authors[which(authors == "Concepción Ornosa, Félix Torres & Pilar de la Rúa")] <- "Concepción Ornosa, Félix Torres, Pilar de la Rúa"
authors[which(authors == "Castro, L.")] <- "L. Castro"
authors[which(authors == "Ortiz-Sanchez, F. J., Ornosa, C.")] <- "F.J. Ortiz-Sanchez, C. Ornosa"
authors[which(authors == "Banaszak, J., Ortiz-Sanchez, F. J.")] <- "J. Banaszak, F.J. Ortiz-Sanchez"
authors[which(authors == "C. Ornosa, F. Torres & F. J. Ortiz-Sánchez")] <- "C. Ornosa, F. Torres, F. J. Ortiz-Sánchez"

author_pool <- stri_paste(authors, collapse = ",")
author_list <- unlist(strsplit(author_pool, ","))
author_list <- trimws(author_list)
#sort(unique(author_list))[-1] #79 contributors!
#write.csv(sort(unique(author_list))[-1], "data/authors.csv")

auth <- c(
"Alejandro Núñez"
,"Amparo Lázaro"
,"Ana Montero-Castaño"
,"Anna Traveset"
,"Blanca Arroyo-Correa"
,"C. Heras"
,"Curro Molina"
,"C. O’Connor"
,"Concepción Ornosa"
,"C. Pérez-Iñigo Mora"
,"Carlos Lara-Romero"
,"T. Wood"
,"Concepción Ornosa"
,"Concepción Ornosa"
,"D. Paredes"
,"D. Romero"
,"David Alomar"
,"F. Javier Ortiz-Sánchez"
,"F. Javier Ortiz-Sánchez"
,"F. López-Núñez"
,"F. Perfectti"
,"Félix Torres"
,"F. Javier Ortiz-Sánchez"
,"Félix Torres"
,"F. Javier Ortiz-Sánchez"
,"H. Gaspar"
,"Ignasi Bartomeus"
,"Isabel María Liberal"
,"Isabel María Liberal"
,"J. Ascher"
,"J. Banaszak"
,"J. Bosch"
,"J. Dusmet"
,"J. Gonzalez-Varo"
,"J. L. Blanco-Pastor"
,"J. Loureiro"
,"J. R. Obeso"
,"J.A. González"
,"J. Bosch"
,"J.D. Alche"
,"J.D. Asís"
,"J.M. Gómez"
,"Javier Herrera"
,"Javier Morente-López"
,"Joana Costa"
,"José Iriondo"
,"Jose Luis Blanco-Pastor"
,"Juan Arroyo"
,"L. Castro"
,"Luis Navarro"
,"M. Campos"
,"M. Miñarro"
,"M. Porcel"
,"M.D. Martínez"
,"M.J. Dardón"
,"M.L. Fernández"
,"Montserrat Vilà"
,"Manuel Baena"
,"Marina Alonso Solano"
,"Mario Fernández-Mazuecos"
,"Carlos Martínez-Núñez"
,"Miguel A. González-Estévez"
,"Montserrat Vilà"
,"Pablo Vargas"
,"Pablo Vargas"
,"Pedro Coello"
,"Pilar de la Rúa"
,"R. Alcalá"
,"R. Carvalho"
,"R. Heleno"
,"P.J. Rey"
,"S. Castro"
,"S. Castro"
,"S.F. Gayubo"
,"Victoria Ferrero"
,"Volker Haeseler")

unique(auth)
```

>>>>

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
#table of
#Name	
#Contact	
#Number of records as main dataholder	
#Number of records as co-dataholder
#email?? Maually :(
#default <- par()$mar
#par(mar = c(13.1, 4.1, 4.1, 2.1))
#barplot(head(sort(table(data2$Authors.to.give.credit), decreasing = TRUE),20), las = 2, cex.names = 0.7)
#par(mar = default)
#Can be done prettier.
#Ideally, we can merge all authors, split and count individually.
library(stringi)
authors <- data$Authors.to.give.credit[which(!is.na(data$Authors.to.give.credit))]
authors[which(authors == "Ornosa, C., Martínez, M. D.")] <- "C. Ornosa, M.D. Martínez"
authors[which(authors == "C. Ornosa & F. J. Ortiz-Sánchez")] <- "C. Ornosa, F. J. Ortiz-Sánchez"
authors[which(authors == "C. Ornosa & M.D. Martínez")] <- "C. Ornosa, M.D. Martínez"
authors[which(authors == "Ortiz-Sanchez, F.J.")] <- "F.J. Ortiz-Sanchez"
authors[which(authors == "Heras, C., Gayubo, S. F.")] <- "C. Heras, S.F. Gayubo"
authors[which(authors == "Ornosa, C.")] <- "C. Ornosa"
authors[which(authors == "Herrera, J.")] <- "Javier Herrera"
authors[which(authors == "Francisco Javier Ortiz-Sánchez, Pedro Coello & Manuel Baena")] <- "Francisco Javier Ortiz-Sánchez, Pedro Coello, Manuel Baena"
authors[which(authors == "González, J. A., Torres, F., Gayubo, S. F.")] <- "J.A. González, , F. Torres, S.F. Gayubo"
authors[which(authors == "Dardón, M. J., Torres, F., Asís, J. D.")] <- "M.J. Dardón, F. Torres, J.D. Asís"
authors[which(authors == "Pérez-Iñigo Mora, C.")] <- "C. Pérez-Iñigo Mora"
authors[which(authors == "Pablo Vargas, Concepción Ornosa, Francisco Javier Ortiz-Sánchez & Juan Arroyo")] <- "Pablo Vargas, Concepción Ornosa, Francisco Javier Ortiz-Sánchez, Juan Arroyo"
authors[which(authors == "C. Heras y S.F. Gayubo")] <- "C. Heras, S.F. Gayubo"
authors[which(authors == "J. L. BLANCO-PASTOR, C. ORNOSA, D. ROMERO, I. M. LIBERAL, J. M. GÓMEZ & P. VARGAS")] <- "J. L. Blanco-Pastor, C. Ornosa, D. Romero, I.M. Liberal, J.M. Gómez, P. Vargas"
authors[which(authors == "Concepción Ornosa, Félix Torres & Pilar de la Rúa")] <- "Concepción Ornosa, Félix Torres, Pilar de la Rúa"
authors[which(authors == "Castro, L.")] <- "L. Castro"
authors[which(authors == "Ortiz-Sanchez, F. J., Ornosa, C.")] <- "F.J. Ortiz-Sanchez, C. Ornosa"
authors[which(authors == "Banaszak, J., Ortiz-Sanchez, F. J.")] <- "J. Banaszak, F.J. Ortiz-Sanchez"
authors[which(authors == "C. Ornosa, F. Torres & F. J. Ortiz-Sánchez")] <- "C. Ornosa, F. Torres, F. J. Ortiz-Sánchez"
author_pool <- stri_paste(authors, collapse = ",")
author_list <- unlist(strsplit(author_pool, ","))
author_list <- trimws(author_list)
#sort(unique(author_list))[-1] #79 contributors!
#write.csv(sort(unique(author_list))[-1], "data/authors.csv")
auth <- c(
"Alejandro Núñez"
,"Amparo Lázaro"
,"Ana Montero-Castaño"
,"Anna Traveset"
,"Blanca Arroyo-Correa"
,"C. Heras"
,"Curro Molina"
,"C. O’Connor"
,"Concepción Ornosa"
,"C. Pérez-Iñigo Mora"
,"Carlos Lara-Romero"
,"T. Wood"
,"Concepción Ornosa"
,"Concepción Ornosa"
,"D. Paredes"
,"D. Romero"
,"David Alomar"
,"F. Javier Ortiz-Sánchez"
,"F. Javier Ortiz-Sánchez"
,"F. López-Núñez"
,"F. Perfectti"
,"Félix Torres"
,"F. Javier Ortiz-Sánchez"
,"Félix Torres"
,"F. Javier Ortiz-Sánchez"
,"H. Gaspar"
,"Ignasi Bartomeus"
,"Isabel María Liberal"
,"Isabel María Liberal"
,"J. Ascher"
,"J. Banaszak"
,"J. Bosch"
,"J. Dusmet"
,"J. Gonzalez-Varo"
,"J. L. Blanco-Pastor"
,"J. Loureiro"
,"J. R. Obeso"
,"J.A. González"
,"J. Bosch"
,"J.D. Alche"
,"J.D. Asís"
,"J.M. Gómez"
,"Javier Herrera"
,"Javier Morente-López"
,"Joana Costa"
,"José Iriondo"
,"Jose Luis Blanco-Pastor"
,"Juan Arroyo"
,"L. Castro"
,"Luis Navarro"
,"M. Campos"
,"M. Miñarro"
,"M. Porcel"
,"M.D. Martínez"
,"M.J. Dardón"
,"M.L. Fernández"
,"Montserrat Vilà"
,"Manuel Baena"
,"Marina Alonso Solano"
,"Mario Fernández-Mazuecos"
,"Carlos Martínez-Núñez"
,"Miguel A. González-Estévez"
,"Montserrat Vilà"
,"Pablo Vargas"
,"Pablo Vargas"
,"Pedro Coello"
,"Pilar de la Rúa"
,"R. Alcalá"
,"R. Carvalho"
,"R. Heleno"
,"P.J. Rey"
,"S. Castro"
,"S. Castro"
,"S.F. Gayubo"
,"Victoria Ferrero"
,"Volker Haeseler")
print(unique(auth))
